%!TEX root = proposal.tex

\section{Related Work}

% \chenhao{cite more CHI work here}

Collaborative writing has attracted significant interest from computer science for decades as writing is increasingly a digitalized process \citep{sharples1993research}.
In particular, researchers have worked on understanding the practice of collaborative writing  \citep{birnholtz2013write,wang2017users} and exploring the feasibility of crowdsourcing by splitting the writing process into micro tasks \citep{bernstein2010soylent,teevan2016supporting,salehi2017communicating}. 
Thanks to the recent progress in AI enabled by deep learning, researchers started to explore the role of intelligent support in writing \citep{gehrmann2015deploying}, include PI Tan's prior work \citep{clark+etal18}, which we will elaborate to provide the context for this work.

\para{Prior work.} We conducted a pilot study with 18 participants in \citet{clark+etal18} on slogan writing.
% \chenhao{feel free to shorten this part.}
% Slogan writing presents a challenge to writers that is similar to humor generation: to generate a concise, memorable, and powerful sentence that is representative of the object it promotes and matches the intention of the authors. 
% Slogans are used for promotion in a variety of settings, ranging from organizing a social movement to promoting a product. 
% Success in machine-in-the-loop systems for slogan writing and humor generation can lead to potential paradigm changes in many domains of creative writing.
% a system that supports slogan writing could be extended to several related tasks that prioritize catchy and succinct language.
We asked all participants to write slogans for three scenarios (food packaging tool,
the movie ``Her'', and a social cause that protests animal testing
for cosmetic products).
Half of them wrote with a machine in the loop ({\em treatment}), while the other half wrote on their own ({\em control}).
We asked participants to assess the writing process and their final slogans, and answer open-ended questions in an interview.
We also collected third-party evaluations of each slogan from Amazon Mechanical Turk.
% The machine learning system adopts an iterative design that is not intrusive and uses pull-based suggestions.
Overall, our preliminary findings suggest that machine-in-the-loop systems for creative writing are promising: 1) participants generally found the writing process more engaging and more fun with a machine in the loop;
2) participants with a machine in the loop generally rated their own slogans better than the control group (although there is no difference in third-party evaluation).
These results motivate us to pursue machine-in-the-loop collaborative writing.
% , however, the computational model requires improvement. 
% Here we highlight the most relevant findings.
% % Our results show that (for space reasons, including only three findings):


% \begin{enumerate}[leftmargin=*,noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
%     \item Users generally found the writing process more engaging and more fun with a machine in the loop.
%     \item Users with a machine in the loop generally rated their own slogans better than the control group, but there is no difference in third-party evaluation.
%     \item Users gave low ratings to the suggestions in every aspect, especially regarding relevance (see \figref{fig:user}).
% \end{enumerate}

% We draw insights from quantitative ratings from participants and qualitative interviews with users to improve our machine learning systems that generate suggestions.
% To motivate our proposed ideas in this proposal, we give a brief overview of the computational model in the slogan writing machine learning system.
Since this study focuses on individual writing, the main implication for this proposal lies in the content suggestion part. 
% In addition to focusing on individual writing, another key difference from this proposal is that the machine learning system generates {\em full-sentence suggestions}.
% However, 
Many participants point out in the interviews that keyword suggestions may be much more useful than full-sentence suggestions used in this study, partly due to the difficulty of generating high-quality full sentences and the fact that stopwords and syntactic structure in full sentences are less useful for humans.
