%!TEX root = proposal.tex

\section{Researcher roles, Timeline, and Use of Funds}

\para{Researcher roles.}
PI Tan will lead the design of computational algorithms and models required to offer suggestions in the collaborative writing process;
PI Yin will lead the design and development of online experiments.
We expect our graduate students to work closely on every component of this proposal.
We will make sure that the PIs and graduate students meet regularly to seamlessly integrate research efforts at two Universities.
The PIs are expected to spend a month over the summer and one week per day over the academic year on this project.


\para{Timeline.} We expect an approximate timeline as follows.

\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
    \item 01/2020 --- 06/2020. Collect relevant data, develop required algorithms, models, and webapps.
    \item 07/2020 --- 10/2020. Pilot initial experiments and refine the algorithms using slogan writing.
    \item 11/2020 --- 01/2021. Extend results to other writing tasks and further refine the design of algorithms, models, and webapps.
    \item 02/2020 --- 05/2021. Finish all experiments, and prepare manuscripts and demos to disseminate the research outcomes.
\end{itemize}

\para{Use of funds.} We request \$250,000 in total, which will be evenly split between these two University.
The Colorado part will be used for the following purposes:
1) a graduate student support including benefits for a year and a half (\$88,359);
2) one month summary salary including benefits for PI Tan (\$15,832);
3) travel to Redmond (\$3,616);
4) User study (\$17,193).
\chenhao{add Ming's budget here.}
In addition, we request \$150,000 Azure credits for developing computational models and hosting the webapp for collaborative writing.


\para{Resources.} We will consider using the ``Data Set of English-Spanish Term Vectors from Wikipedia'' in Microsoft Research Open Data. 
If possible, it would be useful to share existing collaborative writing datasets in Microsoft, either from Office 365 or Microsoft Teams.

\para{Other support.} 
We have our startup package to supplement user study if the budget is insufficient.
In addition to the required visit, we can visit Microsoft for two weeks to a month over the summer.

